Cover letter for the original IJRR submission

### 2017-10-06 reviews_tro/reviewer_response.tex

\as{Agreed. We removed the incriminated text and provided an intuition of the heuristic in the text, as mentioned above.}\done

\quot{github link seems to be dead? (The link on p. 15 is OK\dots should they be the same?)}

\as{We are suprised by this comment because after testing it, the link seems to be valid. In any case, in accordance with reviewer 6, we changed all the links source codes to provide a SHA link that will bring the user to the accurate revision of the projects considered.}
\qt{(Section VII) Both HPP and our planner can be simply downloaded and compiled by following the instructions on
\url{https://humanoid-path-planner.github.io/hpp-doc/download.html?branch=rbprm}. \\
(Appendix C) To address the other scenarios, we propose a new implementation, entirely open source (\url{https://github.com/stonneau/python_sandbox/releases/tag/tro_paper} ), which can be integrated directly in our motion planner software. }\done

\quot{p.5, on right, ``less than epsilon'' between end effector and world - but doesn’t the orientation of the end effector matter tremendously here, too?}
\as{
We agree that the orientation of the end effector matters. Indeed, we could consider to further filter the set of candidates samples regarding orientation, to reduce the number of failed
projections. However, because of the joint limits constraints, computing a relevant orientation distance is less trivial than in the 3D case. We tried to implement this
in earlier versions of the planner, and did not obtain significant gains in the performance. We believe it is explained by the fact that the majority of unfeasible samples is already
efficiently rejected by the simple ``epsilon distance'' check. We updated the text of the paper to explain this.
}
\qt{Because the distance $\epsilon$ does not account for the variation in orientation, several samples of $ C_{Contact}^{\epsilon}$  may turn out to be unfeasible at the time of projection. One could consider additionally filtering $ C_{Contact}^{\epsilon}$ based on the orientation with respect to the obstacle normal, but in our experience we did not notice
any major improvement in the computational performances of the planner, so we do not perform this additional step. }
%~ Using an epsilon is an effective way to remove many irrelevant configurations.  and
%~ we believe that more complex solutions aiming at taking into account the orientation would end up being counter productive.
 %~ Indeed, using only 3D distance, we will end up with a few configurations
%~ that can't be projected correctly, and will end up being discarded. But the majority of irrelevant configurations would already have been rejected with
%~ the efficient 3D intersection query. Introducing additional filtering . } 
\done

### 2017-10-06 body/contact.tex
typo

%~ The reader is referred to our previous work for an extensive discussion on the benefits of this approach, and the optimal choice 
%~ of the parameter $N$~\citep{Tonneau2014}. Our criterion to assert efficiently the static equilibrium of the robot, as well as the heuristics $h$ are detailed in Appendix~\ref{sec:heuristics}.
Because the distance computation $\epsilon$ does not account for the variation in orientation, several samples of $ C_{Contact}^{\epsilon}$  may turn out to be unfeasible at the time of projection. One could consider additionally filtering $ C_{Contact}^{\epsilon}$ based on the orientation with respect to the obstacle normal, but in our experience we did not notice
any major improvement in the computational performances of the planner, so we do not perform this additional step.

>>>>

%~ The reader is referred to our previous work for an extensive discussion on the benefits of this approach, and the optimal choice 
%~ of the parameter $N$~\citep{Tonneau2014}. Our criterion to assert efficiently the static equilibrium of the robot, as well as the heuristics $h$ are detailed in Appendix~\ref{sec:heuristics}.
Because the distance $\epsilon$ does not account for the variation in orientation, several samples of $ C_{Contact}^{\epsilon}$  may turn out to be unfeasible at the time of projection. One could consider additionally filtering $ C_{Contact}^{\epsilon}$ based on the orientation with respect to the obstacle normal, but in our experience we did not notice
any major improvement in the computational performances of the planner, so we do not perform this additional step.
